Millions of Type Errors

### 2023-09-12 programming23/paper.tex
More citations

Beyond their immediate applications to {Lua},
answers to these questions have implications for the design
of gradual types, success types, and semantic subtyping.
Luau represents the first large-scale combination of these features,
and lessons from this experience can inform future applications.

>>>>

Beyond their immediate applications to {Luau},
answers to these questions have implications for the design
of gradual types~\cite{st-sfp-2006}, success types~\cite{lindahl2006practical},
and semantic subtyping~\cite{CF05:GentleIntroduction,Jef22:SemanticSubtyping}.
Luau represents the first large-scale combination of these features,
and lessons from this experience can inform future applications.
